Vibronic Coupling Effects in the Photoelectron Spectrum of Ozone: A Coupled-Cluster Approach

### 2024-08-23 article.tex
Turn the document into single-spaces
Update to the summary from Dr. Stanton

\documentclass[12pt,a4paper,prb,aps,superscriptaddress]{revtex4}
\usepackage{amsmath,amssymb,physics}
\usepackage{graphicx} % For figures with images
\usepackage{natbib} % bibliography
\setcitestyle{super, sort&compress, comma} % chemistry style
\usepackage{hyperref} % Clickable links in the document and their colors
\hypersetup{
    colorlinks=true, % false: boxed links; true: colored links
    linkcolor=cyan, % color of internal links
    citecolor=magenta, % color of links to bibliography
    filecolor=magenta, % color of file links
    urlcolor=cyan, % color of external links
    runcolor=cyan
}

@@

We have simulated the vibronic effects in the photoelectron spectrum of the
ozone.  We have used the KDC Hamiltonian\cite{Cederbaum:LVC:84, KDC:81,
Koppel:CIbookCh7:04} with the \emph{ab initio} parametrisation of the
quasi-diabatic states of Ichino, Gauss and Stanton.~\cite{Stanton:EOMIPdeg:09}
The results of our simulation match well the photoelectron spectrum from
1970s~\cite{dyke:O3:74} and the PFI-ZEKE spectrum from
2005.~\cite{Willitsch:O3ZEKE:2005} We present analysis of the spectra and
highlight the role of the vibronic coupling effects. Our simulation offers a
state-of-the-art insight into the spectrum and allows us to assign the
simulated peaks. Our assignment agrees well with the previously assigned
progression in the symmetric bend but we reassign some of the other features
of the spectrum. Simulated peaks that gain intensity from the B$_2$ state are
absent in the PFI-ZEKE spectrum which offers an interesting avenue for further
investigations. Modeling of the intensity of the PFI-ZEKE peaks is not
unlikely to bring insight into this problem.  Additionally our simulation does
not model dissociation of the ozone cation, which will play a role in the high
energy part of the spectrum.

>>>>

\documentclass[
12pt,
a4paper,
prb,
superscriptaddress,
tightenlines,  % single-spaced
]{revtex4}
\usepackage{amsmath,amssymb,physics}
\usepackage{graphicx} % For figures with images
\usepackage{natbib} % bibliography
% \setcitestyle{super, sort&compress, comma} % chemistry style (prb's default)
\usepackage{hyperref} % Clickable links in the document and their colors
\hypersetup{
    colorlinks=true, % false: boxed links; true: colored links
    linkcolor=cyan, % color of internal links
    citecolor=magenta, % color of links to bibliography
    filecolor=magenta, % color of file links
    urlcolor=cyan, % color of external links
    runcolor=cyan
}

@@

In this exploration of the photoelectron spectrum of the ozone molecule,
cutting-edge high-order coupled cluster models have been used together with a
vibronic Hamiltonian approach to spectroscopy beyond the Born-Oppenheimer
approximation \cite{Cederbaum:LVC:84, KDC:81, Koppel:CIbookCh7:04}.
Calculations based on the equation-of-motion method known as EOMIP-CC have
been used to parametrize the Hamiltonian, which relies importantly on the
quasi-diabatic states of Ichino, Gauss and Stanton.~\cite{Stanton:EOMIPdeg:09}
The results of the simulation provide an excellent match to the experimental
spectrum from the ionization potential of the lower state to about 2500
cm$^{-1}$ higher (the restriction arising from the local parametrization of
the Hamiltonian).  Analysis of the spectrum and its simulation underscore the
importance of vibronic coupling effects in the ozone cation.  Results of this
work offer a state-of-the-art insight into the spectrum and allows for an
assignment of the experimental results.  Simulated peaks that gain intensity
from the ${\tilde A}B_2$ state are absent in the PFI-ZEKE spectrum which
offers an interesting avenue for further investigations.
